---
title: "Case Message Study Script"
output: html_document
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
---

#Libraries
```{r}
library(tidyverse)
library(patchwork)
library(lme4)
library(lmerTest)
library(psych)
library(effectsize)
library(mediation)
library(car)
library(stringdist)
library(clue)
library(afex)
library(sjPlot)
library(emmeans)

#for the notation
options(scipen=999)
```

#STUDY 1

##Study 1: Load and clean data
```{r}
#Study 1a
d.p <- read.csv("Study1a.csv") %>% 
  filter(Finished == 1)

d1a <- d.p %>%
  filter(att == "4" | is.na(att)) %>% 
  filter(att.1 == "4" | is.na(att.1)) %>% 
  pivot_longer(cols = starts_with(c("a.", "i.", "u.", "p.", "v.")),
               names_to = c(".value", "category"),
               names_sep = "\\.",
               values_drop_na = TRUE) %>% 
  dplyr::select(id, category, a, i, u, p, v) %>% 
  mutate(category = dplyr::recode(category,
                           "g1" = "general 1",
                           "g2" = "general 2",
                           "n1" = "narrative 1",
                           "n2" = "narrative 2")) %>% 
  separate(col = category, into = c("condition", "time"), sep = " ") %>%
  mutate(condition = as.factor(condition), time = as.factor(time)) %>% 
  mutate(x = (a+i+u+p+v)/5) %>% 
  mutate(condition = dplyr::recode(condition,
                            "general" = "message",
                            "narrative" = "case"))

#Study 1b
#Data from Part 2
i.p <- read.csv("Study1b.csv") %>% 
  filter(Finished == 1)

d1b <- i.p %>%
  filter(if_any(contains("att"), ~.x == "4" | is.na(.x))) %>% 
  pivot_longer(cols = contains(c("_a", "_i", "_u", "_p", "_v")),
               names_to = c(".item", "category"),
               names_sep = "\\_",
               values_drop_na = TRUE) %>% 
  filter(category != "att") %>% 
  mutate(category = substr(category, 1, 1)) %>% 
  spread(key = category, value = value) %>% 
  mutate(x = (a+i+u+p+v)/5) %>% 
  mutate(summary = as.factor(.item)) %>%
  dplyr::select(-.item) %>% 
  rename(condition = FL_77_DO)
```


###Study 1: Analyze
```{r}
# # # # Preregistered # # # #
p_values <- list()

#initial
#c1 vs m1
d.time1 <- d1a %>% 
  filter(time == 1)
m1 <- t.test(x ~ condition, d.time1)
m1
cohens_d(x ~ condition, data = d.time1)
p_values$m1 <- m1$p.value

#paired
#c1 vs c2
d.c <- d1a %>% 
  filter(condition == "case")
m2 <- t.test(x ~ time, d.c, paired = T)
m2
cohens_d(x ~ time, data = d.c)
p_values$m2 <- m2$p.value

#m1 vs m2
d.m <- d1a %>% 
  filter(condition == "message")
m3 <- t.test(x ~ time, d.m, paired = T)
m3
cohens_d(x ~ time, data = d.m)
p_values$m3 <- m3$p.value

#c2 vs m2
d.time2 <- d1a %>% 
  filter(time == 2)
m4 <- t.test(x ~ condition, d.time2)
m4
cohens_d(x ~ condition, data = d.time2)
p_values$m4 <- m4$p.value

#unpaired
#c3 vs m3
m5 <- t.test(x ~ condition, d1b)
m5
cohens_d(x ~ condition, data = d1b)
p_values$m5 <- m5$p.value

#corrected p-values
p.adjust(p_values, method = "holm")

# # # # Exploratory # # # #
#Part 1 full scale analysis
m <- lmer(x ~ condition * time + (1|id), d1a)
summary(m)
emm_int <- emmeans(m, pairwise ~ condition | time)
eff_size(emm_int, sigma = sd(d1a$x), edf = df.residual(m))

#Part 2 with item properly added as a random variable
m <- lmer(x ~ condition + (1|summary), d1b)
summary(m)
standardized_result <- standardize_parameters(m)
print(standardized_result)

# # # Scale validation # # #
items <- d1a[, c("a", "u", "v", "i", "p")]
alpha(items)

items <- d1b[, c("a", "u", "v", "i", "p")]
alpha(items)
```

##Study 1: Visualize
```{r}
#merge datasets
d1b <- dplyr::select(d1b, -summary)
d1b$time <- 3
d1b$time <- as.factor(d1b$time)
d1_visualization <- bind_rows(d1a, d1b)

#rename levels
d1_visualization$time <- factor(d1_visualization$time, labels = c("initial rating", "second rating", "judges' rating of actual insight"))

#set order
ggplot(d1_visualization, aes(x = time, y = x, color = condition, group = condition)) +
  geom_point(position = position_jitter(width = 0.2, height = 0.15), size = 4, alpha = 0.15) +
  stat_summary(fun = mean, geom = "line", linewidth = 1.25, alpha = 0.6) +
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width = 0, linewidth = 1.5, alpha = 0.8) +
  stat_summary(fun = mean, geom = "point",  aes(shape = condition), size = 3, fill = "white", stroke = 1) +
  scale_color_manual(values = c("message" = "#4C72B0", "case" = "#55A868")) +
  scale_shape_manual(values = c("message" = 21, "case" = 23)) + 
  scale_y_continuous(expand = expansion(mult = c(0, 0.05))) +
  labs(x = "", y = "Mean Insight Score", title = "") +
  theme_minimal() +
  theme(
    legend.position = "top", 
    legend.title = element_blank(),
    text = element_text(size = 14, family = "Arial"),
    axis.title.x = element_text(margin = margin(t = 10)),
    axis.title.y = element_text(margin = margin(r = 10))
  )
```












#STUDY 2

##Study 2: Load and clean datasets
```{r}
#Study 2a
d.p <- read.csv("Study2a.csv") %>% 
  filter(Finished == 1)

d2a <- d.p %>%
  filter(att_t == "4" | is.na(att_t)) %>% 
  filter(att_s == "4" | is.na(att_s)) %>% 
  dplyr::select(-q_s_DO, -q_t_DO) %>% 
  pivot_longer(cols = starts_with(c("a.", "i.", "u.", "p.", "v.", "q_")),
               names_to = c(".value", "stimulus_set"),
               names_sep = "\\_",
               values_drop_na = TRUE) %>% 
  pivot_longer(cols = starts_with(c("a.", "i.", "u.", "p.", "v.")),
               names_to = c(".value", "condition"),
               names_sep = "\\.",
               values_drop_na = TRUE) %>% 
  dplyr::select(stimulus_set, condition, a, i, u, p, v, q) %>% 
  mutate(condition = dplyr::recode(condition,
                           "c1" = "case",
                           "m1" = "message")) %>% 
  mutate(condition = as.factor(condition)) %>% 
  mutate(x = (a+i+u+p+v)/5) %>% 
  mutate(stimulus_set = dplyr::recode(stimulus_set,
                            "s" = "Semmelweis",
                            "t" = "Dominos"))
  
#Study 2b
i.p <- read.csv("Study2b.csv") %>% 
  filter(Finished == 1)

d2b <- i.p %>%
  pivot_longer(cols = contains(c("a.", "i.", "u.", "p.", "v.", "att")),
             names_to = c("report", "question", "stimulus_set"),
             names_sep = "_",
             values_drop_na = TRUE) %>% 
   separate(question, into = c("question", "condition"), sep = "\\.", extra = "merge") %>% 
  spread(key = question, value = value) %>% 
  filter(att == 4) %>% 
  mutate(x = (a+i+u+p+v)/5) %>% 
  mutate(report = paste(report, condition, stimulus_set, sep = "")) %>% 
  mutate(summary = as.factor(report)) %>% 
  mutate(condition = dplyr::recode(condition,
                           "c" = "case",
                           "m" = "message")) %>% 
  mutate(condition = as.factor(condition)) %>%
  mutate(stimulus_set = dplyr::recode(stimulus_set,
                            "s" = "Semmelweis",
                            "d" = "Dominos"))
```

##Study 2: Analyze data
```{r}
# # # # Preregistered # # # #
p_values <- list()

#Part 1
#x ~ condition*stimulus_set
#type iii anova
m <- Anova(lm(x ~ condition * stimulus_set, data = d2a), type = 3)
m
effect_sizes <- eta_squared(m, partial = TRUE)
effect_sizes

#interaction insignificant -> type ii anova
m <- Anova(lm(x ~ condition * stimulus_set, data = d2a), type = 2)
m
effect_sizes <- eta_squared(m, partial = TRUE)
effect_sizes

#q ~ condition*stimulus_set
m <- glm(q ~ condition*stimulus_set, family = "binomial", d2a)
summary(m)
#effect size
tab_model(m, transform = "exp")

#Part 2
#x ~ condition*stimulus_set + summary
m <- lmer(x ~ condition*stimulus_set + (1|summary), d2b)
summary(m)
# Standardized coefficients
standardized_result <- standardize_parameters(m)
print(standardized_result)

#corrected p-values for case-message comparisons
p <- c(0.001735, 0.0478, 0.3468)
p.adjust(p, method = "holm")

# # # # Exploratory # # # #
#Part 1
#x ~ condition*stimulus_set
m <- lmer(x ~ condition + (1|stimulus_set), d2a)
summary(m)
# Standardized coefficients
standardized_result <- standardize_parameters(m)
print(standardized_result)

#q ~ condition*stimulus_set
m <- glmer(q ~ condition + (1|stimulus_set), family = "binomial", d2a)
summary(m)
#effect size
tab_model(m, transform = "exp")


#Part 2
#x ~ condition*stimulus_set + report
m <- lmer(x ~ condition + (1|stimulus_set) + (1|summary), d2b)
summary(m)
# Standardized coefficients
standardized_result <- standardize_parameters(m)
print(standardized_result)
```

##Study 2: Visualize data
```{r}
#merge datasets
d2a$rating <- 1
d2b$rating <- 2
d2_visualization <- bind_rows(d2a, d2b)

#set order
d2_visualization <- d2_visualization %>% 
  mutate(rating = case_when(rating == 1 ~ "participant perceptions of insight",
                            rating == 2 ~ "judges' rating of actual insight"))
d2_visualization$rating <- factor(d2_visualization$rating, levels = c("participant perceptions of insight", "judges' rating of actual insight"))
d2_visualization$condition <- factor(d2_visualization$condition, levels = c("message", "case"))


p1 <- ggplot(d2_visualization, aes(x = stimulus_set, y = x, fill = condition)) +
  geom_violin(alpha = 0.1, color = NA, position = position_dodge(width = 0.8)) +
  geom_point(aes(color = condition), position = position_jitterdodge(jitter.width = 0.3, jitter.height = 0.1, dodge.width = 0.8), 
             size = 3.5, shape = 21, alpha = 0.2) +
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width = 0, color = "black", linewidth = 1.5,
               position = position_dodge(width = 0.8), aes(group = condition)) +
    stat_summary(fun = mean, geom = "point",
               aes(shape = condition),
               size = 3, color = "black", fill = "white",
               position = position_dodge(width = 0.8)) +
  scale_shape_manual(values = c("message" = 21, "case" = 23)) +
  facet_wrap(~rating) +
  scale_fill_manual(values = c("message" = "#A51C30", "case" = "#666666")) +
  scale_color_manual(values = c("message" = "#A51C30", "case" = "#666666")) +
  labs(x = "", y = "Mean Insight Score", title = "A. Insight Ratings") +
  theme_minimal() +
  theme(
    legend.position = "none",
    text = element_text(size = 14, family = "Arial"),
    plot.title = element_text(face = "bold", hjust = 0.5),
    axis.title.x = element_text(margin = margin(t = 10)),
    axis.title.y = element_text(margin = margin(r = 10)),
    strip.text = element_text(face = "bold")
  )

#summarize data to calculate the proportion of 1's in q
d2a_summary <- d2a %>%
  group_by(stimulus_set, condition) %>%
  summarise(
    proportion_correct = mean(q),
    n = n(),
    se = sqrt(proportion_correct * (1 - proportion_correct) / n),
    ci_low  = pmax(0, proportion_correct - 1.96 * se),
    ci_high = pmin(1, proportion_correct + 1.96 * se),
    .groups = "drop"
  )

d2a_summary$condition <- factor(d2a_summary$condition, levels = c("message", "case"))

#plot the data
p2 <- ggplot(d2a_summary, aes(x = stimulus_set, y = proportion_correct, fill = condition)) +
  geom_col(position = position_dodge(width = 0.8), color = "#D3D3D3", alpha = 0.15) +
  geom_errorbar(
    aes(ymin = ci_low, ymax = ci_high, group = condition), 
    position = position_dodge(width = 0.8),
    width = 0,
    linewidth = 1.5,
    color = "black"
  ) +
  geom_point(aes(shape = condition),
             position = position_dodge(width = 0.8),
             size = 3, stroke = 0.5,
             fill = "white", color = "black",
             show.legend = c(fill = FALSE, shape = TRUE)) +
  scale_fill_manual(values = c("message" = "#A51C30", "case" = "#666666")) +
  scale_shape_manual(values = c("message" = 21, "case" = 23)) +
  labs(x = "", y = "Proportion of correct scores on quiz", title = "B. Quiz Performance") +
  theme_minimal() +
  theme(
    legend.position = "right",
    legend.title = element_blank(),
    text = element_text(size = 14, family = "Arial"),
    plot.title = element_text(face = "bold", hjust = 0.5),
    axis.title.x = element_text(margin = margin(t = 10)),
    axis.title.y = element_text(margin = margin(r = 10)),
    strip.text = element_text(face = "bold")
  )

#combine plots
p1 + p2 + plot_layout(ncol = 2, widths = c(1, 0.2))
```







#Study 3

##Study 3a

###Study 3a: Load and clean data

NOTE: THIS CHUNK WILL NOT RUN, BECAUSE STUDY 3 HAD TO BE MADE ANONYMOUS. INSTEAD, REFER TO NEXT CHUNK.

```{r}
# Study 5pre
d.p <- read.csv("Study3pre.csv")
d3pre <- d.p %>%
  mutate(across(c(Q1, Q2, Q3, Q4, Q5, Q6), as.numeric)) %>%
  mutate(pre_test_score = (Q1 + Q2 + Q3 + Q4 + Q5 + Q6) / 6) %>% 
  dplyr:: select(name, pre_test_score) %>%
  group_by(name) %>%
  filter(n() == 1) %>%
  ungroup()

# Study 5post
d.p <- read.csv("Study3post.csv")
d3post <- d.p %>%
  mutate(across(c(Q1, Q2, Q3, Q4, Q5, Q6, a, i, u, p, v), as.numeric)) %>% 
  mutate(post_test_score = (Q1 + Q2 + Q3 + Q4 + Q5 + Q6) / 6) %>% 
  mutate(x = (a+i+u+p+v)/5) %>% 
  dplyr::select(name, post_test_score, x, learn) %>% 
  group_by(name) %>%
  filter(n() == 1) %>%
  ungroup()

# Compute full Jaro-Winkler distance matrix
dist_matrix <- stringdistmatrix(d3post$name, d3pre$name, method = "jw")
# solve the "optimal assignment" problem
assignment <- solve_LSAP(dist_matrix)

# Create matched dataset
matched <- tibble(
  post_name = d3post$name,
  pre_name = d3pre$name[assignment],
  distance = diag(dist_matrix[, assignment]),
  post_test_score = d3post$post_test_score,
  pre_test_score = d3pre$pre_test_score[assignment],
  x = d3post$x
) %>%
  mutate(delta = post_test_score - pre_test_score)

# Filter out bad matches
d3 <- matched %>%
  filter(distance < 0.20) %>% 
  # only one clearly inconsistent name "zhang" versus "wang" last name
  filter(post_name != "crystal zhang")

# paired t-test comparing scores on the quiz before and after the lesson
d3_ttest <- d3 %>% 
  pivot_longer(cols = c(pre_test_score, post_test_score),
               names_to = "time",
               values_to = "score")
```

This chunk will run in substitution for the one above
```{r}
# read in anonymous csv
d3 <- read.csv("d3_anonymous.csv")

# remove one inconsistent name (which corresponds to 5)
d3 <- d3 %>%
  filter(post_name != "5")

# make t-test dataframe
d3_ttest <- d3 %>% 
  pivot_longer(cols = c(pre_test_score, post_test_score),
               names_to = "time",
               values_to = "score")
```


###Study 3a: Analyses
```{r}
# effect of lesson on learning general message
m <- t.test(score ~ time, d3_ttest, paired = T)
m
cohens_d(score ~ time, data = d3_ttest)

# a linear mixed effects model testing the correlation between insight ratings and change in quiz scores (with participant id as a random intercept)
# have to deviate from prereg because the random effect is literally unrunable...
m <- lm(x ~ delta, d3)
summary(m)
# Standardized coefficients
standardized_result <- standardize_parameters(m)
print(standardized_result)

# # # # Exploratory # # # #
# remove inattentive students
d3_positive <- d3 %>% 
  filter(delta >= 0)
# analysis
m <- lm(x ~ delta, d3_positive)
summary(m)
# Standardized coefficients
standardized_result <- standardize_parameters(m)
print(standardized_result)
```

##Study 3b

###Study 3b: Load and clean data
```{r}
#Data from Part 2
i.p <- read.csv("Study3b.csv")

d3b <- i.p %>%
  filter(if_any(contains("att"), ~.x == "4" | is.na(.x))) %>%
  pivot_longer(cols = contains(c("_a", "_i", "_u", "_p", "_v")),
               names_to = c(".item", "category"),
               names_sep = "\\_",
               values_drop_na = TRUE) %>%
  filter(category != "att") %>%
  mutate(category = substr(category, 1, 1)) %>%
  spread(key = category, value = value) %>%
  filter(a != "") %>%
  mutate(across(c(a, i, u, p, v), as.numeric)) %>%
  mutate(x = (a+i+u+p+v)/5) %>%
  mutate(summary = as.factor(.item)) %>%
  dplyr::select(-.item) %>%
  rename(condition = FL_4_DO)
```

###Study 3b: Analyses
```{r}
m <- lmer(x ~ condition + (1|summary), d3b)
summary(m)
# Standardized coefficients
standardized_result <- standardize_parameters(m)
print(standardized_result)
```

###Study 3: Visualization
```{r}
# correlation values
cor_test_all <- cor.test(d3$delta, d3$x)
cor_test_positive <- cor.test(d3_positive$delta, d3_positive$x)

# define colors for anonymous school 
sp_colors <- c("Pre Test" = "#00204E", "Post Test" = "#A6192E")
condition_colors <- c("uninsightful" = "#00204E", "insightful" = "#A6192E") 

# define factor levels
d3_ttest <- d3_ttest %>%
  mutate(time = factor(time, levels = c("pre_test_score", "post_test_score"),
                       labels = c("Pre Test", "Post Test")))
d3b <- d3b %>%
  mutate(condition = factor(condition, levels = c("uninsightful", "insightful")))

# Create learning plot
p1 <- ggplot(d3_ttest, aes(x = time, y = score, color = time)) +
  geom_violin(alpha = 0.5) +
  geom_jitter(width = 0.15, alpha = 0.1, size = 5) +
  stat_summary(fun = mean, geom = "line", aes(group = 1), linewidth = 1.5, alpha = 0.8, color = "black") +
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width = 0, linewidth = 2, alpha = 0.8) +
  stat_summary(fun = mean, geom = "point", size = 4, shape = 21, fill = "white", alpha = 1) +
  scale_color_manual(values = sp_colors) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.05))) +
  labs(x = "", y = "Test Score", title = "A. Change in Test Scores") +
  theme_minimal() +
  theme(
    legend.position = "none",
    text = element_text(size = 14, family = "Arial"),
    plot.title = element_text(face = "bold", hjust = 0.5),
    axis.title.x = element_text(margin = margin(t = 10)),
    axis.title.y = element_text(margin = margin(r = 10))
  )

# Create plot 2a (preregistered analysis with all score changes)
corr_text_all <- paste0("r = ", round(cor_test_all$estimate, 2), 
                         ", p = ", scales::pvalue(cor_test_all$p.value, accuracy = 0.001))

p2a <- ggplot(d3, aes(x = delta, y = x)) +
  geom_jitter(width = 0.02, height = 0.1, color = "#00204E", size = 5, alpha = 0.1) +
  geom_smooth(method = "lm", se = TRUE, color = "#A6192E", fill = "#A6192E", alpha = 0.2, linewidth = 1.5) +
  geom_text(
    aes(
      x = 0.6,
      y = 7
    ),
    label = corr_text_all,
    hjust = 1,
    size = 5,
    fontface = "bold",
    color = "black",
  ) +
  labs(x = "Test Score Change", y = "Perceived Insight", 
       title = "B. All Students") +
  theme_minimal() +
  theme(
    text = element_text(size = 14, family = "Arial"),
    plot.title = element_text(face = "bold", hjust = 0.5),
    axis.title.x = element_text(margin = margin(t = 10)),
    axis.title.y = element_text(margin = margin(r = 10))
  )

# Create plot 2b (exploratory analysis with only positive score changes)
corr_text_positive <- paste0("r = ", round(cor_test_positive$estimate, 2), 
                            ", p = ", scales::pvalue(cor_test_positive$p.value, accuracy = 0.001))

p2b <- ggplot(d3_positive, aes(x = delta, y = x)) +
  geom_jitter(width = 0.02, height = 0.1, color = "#00204E", size = 5, alpha = 0.1) +
  geom_smooth(method = "lm", se = TRUE, color = "#A6192E", fill = "#A6192E", alpha = 0.2, linewidth = 1.5) +
  geom_text(
    aes(
      x = 0.7,
      y = 7
    ),
    label = corr_text_positive,
    hjust = 1,
    size = 5,
    fontface = "bold",
    color = "black",
  ) +
  labs(x = "Test Score Change", y = "", 
       title = "Students Who Learned") +
  theme_minimal() +
  theme(
    text = element_text(size = 14, family = "Arial"),
    plot.title = element_text(face = "bold", hjust = 0.5),
    axis.title.x = element_text(margin = margin(t = 10)),
    axis.title.y = element_text(margin = margin(r = 10))
  )


# Plot 3: Third party ratings (study 3b)
d3b_summary <- d3b %>%
  group_by(condition) %>%
  mutate(condition = factor(condition, levels = c("uninsightful", "insightful"))) %>% 
  summarise(
    mean_insight = mean(x, na.rm = TRUE),
    sd = sd(x, na.rm = TRUE),
    n = n(),
    se = sd / sqrt(n),
    lower_ci = mean_insight - qt(0.975, df = n - 1) * se,
    upper_ci = mean_insight + qt(0.975, df = n - 1) * se
  )

p3 <- ggplot() +
  geom_violin(data = d3b, aes(x = condition, y = x, fill = condition), alpha = 0) +
  geom_jitter(data = d3b, aes(x = condition, y = x, color = condition), 
              width = 0.15, alpha = 0.1, size = 5) +
  geom_errorbar(data = d3b_summary, 
                aes(x = condition, ymin = lower_ci, ymax = upper_ci, color = condition),
                width = 0, linewidth = 2, alpha = 0.8) +
  geom_line(data = d3b_summary, 
            aes(x = as.numeric(factor(condition)), y = mean_insight, group = 1),
            linewidth = 1.5, alpha = 0.8, color = "black") +
  geom_point(data = d3b_summary, 
             aes(x = condition, y = mean_insight, color = condition),
             size = 4, shape = 21, fill = "white", alpha = 1) +
  scale_color_manual(values = condition_colors) +
  scale_fill_manual(values = condition_colors) +
  labs(x = "", y = "Perceived Insight", title = "C. Third Party Ratings") +
  scale_y_continuous(expand = expansion(mult = c(0, 0.05))) +
  theme_minimal() +
  theme(
    legend.position = "none",
    text = element_text(size = 14, family = "Arial"),
    plot.title = element_text(face = "bold", hjust = 0.5),
    axis.title.x = element_text(margin = margin(t = 10)),
    axis.title.y = element_text(margin = margin(r = 10))
  )

# Combine all plots using patchwork - side by side
combined_plot <- p1 + p2a + p2b + p3 + 
  plot_layout(ncol = 4, widths = c(1, 1, 1, 1)) +
  plot_annotation(
    title = "",
    theme = theme(plot.title = element_text(size = 16, face = "bold", hjust = 0.5)
    )
  )
```









#STUDY 4

##Study 4a

###Study 4a: Load and clean data
```{r}
df_dirty <- read.csv("Study4a.csv") %>% 
  filter(Finished == 1)

#attention check
df_dirty <- df_dirty %>%
  filter(if_all(starts_with("x"), ~ .x == 4 | is.na(.x) | .x == ""))

data_cleaned <- df_dirty %>%
  dplyr::select(matches("^(v|p|i|u|a)\\.\\d_(s|m|b|f)"), id, z, FL_209_DO)

data_long <- data_cleaned %>%
  pivot_longer(cols = -c(id, z, FL_209_DO),
               names_to = c("question", "type", "stimulus"),
               names_pattern = "(v|p|i|u|a)\\.(\\d)_(.)",
               values_to = "score") %>% 
  filter(score != "")

data_summary <- data_long %>%
  filter(!is.na(score)) %>%
  group_by(id, type, stimulus, z, FL_209_DO) %>%
  summarize(mean = mean(as.numeric(score), na.rm = TRUE), .groups = 'drop')

df <- data_summary %>%
    mutate(stimulus = case_when(
    stimulus == "s" ~ "vienna",
    stimulus == "m" ~ "blockbuster",
    stimulus == "b" ~ "bike",
    stimulus == "f" ~ "merrick"
  )) %>% 
  mutate(temp = case_when(
    type == "1" ~ "message",
    type == "2" ~ "relevant",
    type == "3" ~ "irrelevant"
  )) %>% 
  mutate(type = case_when(
    type %in% c("2", "3") ~ "case",
    type == "1" ~ "message"
  )) %>% 
    group_by(id) %>%
  mutate(condition = case_when(
    any(temp == "relevant") ~ "relevant",
    any(temp == "irrelevant") ~ "irrelevant",
    TRUE ~ "message"
  )) %>%
  ungroup() %>% 
  dplyr::select(-temp)

#Step 5: recode FL_209_DO variable
d4a <- df %>% 
  mutate(report = case_when(
    FL_209_DO == "FL_130" ~ "message",
    FL_209_DO == "FL_332" ~ "message",
    FL_209_DO == "FL_178" ~ "relevant",
    FL_209_DO == "FL_259" ~ "irrelevant",
  ))
```


###Study 4a: Analyze
```{r}
# # # Preregistered # # #
m <- lmer(mean ~ type*condition + (1|stimulus) + (1|id), d4a)
summary(m)
# effect size
standardized_result <- standardize_parameters(m)
print(standardized_result)

# # # Exploratory # # #
#paired
#message v case relevant
d.r <- d4a %>% 
  filter(condition == "relevant")
m <- lmer(mean ~ type + (1|stimulus) + (1|id), d.r)
summary(m)
# effect size
standardized_result <- standardize_parameters(m)
print(standardized_result)

#message v case irrelevant
d.i <- d4a %>% 
  filter(condition == "irrelevant")
m <- lmer(mean ~ type + (1|stimulus) + (1|id), d.i)
summary(m)
# effect size
standardized_result <- standardize_parameters(m)
print(standardized_result)

#ergodicity
d4h <- d4a %>% 
  filter(condition == "relevant") %>% 
  pivot_wider(names_from = "type", values_from = "mean") %>% 
  mutate(difference = case - message) %>% 
  mutate(above = ifelse(case > 6.431382, 1, 0))
  
ggplot(d4h, aes(x = difference, fill = factor(above))) +
  geom_histogram(binwidth = 1.5, position = "dodge", alpha = 0.5) +
  labs(x = "Case - Message Score", y = "Frequency", fill = "Above 1 SD") +
  theme_minimal()

# Get the IDs (or rows) to exclude
high_case_ids <- d4h %>% filter(above == 1) %>% pull(id)

# Filter them out from the long-format data
d.r.below <- d4a %>% 
  filter(condition == "relevant", !id %in% high_case_ids)

m <- lmer(mean ~ type + (1 | stimulus) + (1 | id), data = d.r.below)
summary(m)
standardized_result <- standardize_parameters(m)
print(standardized_result)


#subjects with high insight ratings on the case
#word count
d4a_case <- d4a %>%
  filter(type == "case") %>%
  mutate(above = ifelse(id %in% high_case_ids, 1, 0),
         word_length = nchar(as.character(z)))

m <- lmer(word_length ~ above + (1 | stimulus), data = d4a_case)
summary(m)
standardized_result <- standardize_parameters(m)
print(standardized_result)
```


#Study 4a: Visualize
```{r}
# set factor levels
d4a$type <- factor(d4a$type, levels = c("message", "case"))
d4a$condition <- factor(d4a$condition, levels = c("relevant", "irrelevant"))
d4a$score <- d4a$mean

# create plot
ggplot(d4a, aes(x = type, y = mean, fill = type)) +
  geom_violin(alpha = 0.15, color = "#D3D3D3") +
  geom_point(position = position_jitter(width = 0.2, height = 0.1), 
             size = 3.5, shape = 21, alpha = 0.1) +
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width = 0, color = "#333333", linewidth = 1.5) +
  stat_summary(fun = mean, geom = "line", aes(group = 1), color = "#333333", linewidth = 1.5, alpha = 0.7) +
  stat_summary(fun = mean, geom = "point", size = 3, color = "#333333", shape = 21, fill = "white") +
  facet_wrap(~condition) +
  scale_fill_manual(values = c("message" = "#4C72B0", "case" = "#55A868")) +
  labs(x = "", y = "Mean Insight Score", title = "")+
  theme_minimal() +
  theme(
    legend.position = "none", 
    text = element_text(size = 14, family = "Arial"),
    axis.title.x = element_text(margin = margin(t = 10)),
    axis.title.y = element_text(margin = margin(r = 10)),
    strip.text = element_text(face = "bold")
  )
```

##Study 4b

###Study 4b: Clean
```{r}
df_dirty <- read.csv("Study4b.csv") %>% 
  filter(Finished == 1)

df_dirty <- df_dirty %>%
  filter(if_all(matches("^...x"), ~ .x == 4 | is.na(.x) | .x == ""))

data_cleaned <- df_dirty %>%
  dplyr::select(id, matches("X\\d+_(x|v|p|i|u|a)\\.\\d+_(s|m|b|f)"))

data_long <- data_cleaned %>%
  pivot_longer(cols = -c(id),
               names_to = c("case", "question", "type", "stimulus"),
               names_pattern = "X(\\d+)_(v|p|i|u|a)\\.(\\d)_(.)",
               values_to = "score") %>%
  filter(score != "")

data_summary <- data_long %>%
  filter(!is.na(score)) %>%
  group_by(id, case, type, stimulus) %>%
  summarize(mean = mean(as.numeric(score), na.rm = TRUE), .groups = 'drop')

d4b <- data_summary %>%
    mutate(stimulus = case_when(
    stimulus == "s" ~ "vienna",
    stimulus == "m" ~ "blockbuster",
    stimulus == "b" ~ "bike",
    stimulus == "f" ~ "merrick"
  )) %>%
  mutate(temp = case_when(
    type == "1" ~ "message",
    type == "2" ~ "relevant",
    type == "3" ~ "irrelevant"
  )) %>%
  mutate(temp2 = case_when(
    type %in% c("2", "3") ~ "case",
    type == "1" ~ "message"
  )) %>% 
   mutate(true_case = paste0(case, type, substr(stimulus, nchar(stimulus), nchar(stimulus)))) %>%
  mutate(condition = case_when(
    temp == "relevant" ~ "relevant",
    temp == "irrelevant" ~ "irrelevant",
    TRUE ~ "message"
  )) %>%
  dplyr::select(-type, -temp) %>% 
  rename(type = temp2) %>%
  filter(case != is.na(case))
```


###Study 4b: Analyze
```{r}
# # # # Preregistered # # # #
m <- lmer(mean ~ type*condition + (1|id) + (1|stimulus), d4b)
summary(m)
standardized_result <- standardize_parameters(m)
print(standardized_result)

# post-hoc unpacking of effect
m <- lmer(mean ~ condition + (1|id) + (1|stimulus), d4b %>% filter(condition != "message"))
summary(m)
m <- lmer(mean ~ condition + (1|id) + (1|stimulus), d4b %>% filter(condition != "relevant"))
summary(m)
m <- lmer(mean ~ condition + (1|id) + (1|stimulus), d4b %>% filter(condition != "irrelevant"))
summary(m)
standardized_result <- standardize_parameters(m)
print(standardized_result)

# # # # Exploratory # # # #
m1 <- lmer(mean ~ type*condition + (1|stimulus) + (1|true_case) + (1|id), d4b)
summary(m1)
m2 <- lmer(mean ~ type*condition + (1|stimulus) + (1|true_case), d4b)
summary(m2)
m3 <- lmer(mean ~ type*condition + (1|stimulus) + (1|id), d4b)
summary(m3)
m4 <- lmer(mean ~ type*condition + (1|true_case) + (1|id), d4b)
summary(m4)

AIC(m1)
AIC(m2)
AIC(m3)
AIC(m4)

standardized_result <- standardize_parameters(m4)
print(standardized_result)

# post-hoc unpacking of effect

m5 <- lmer(mean ~ condition + (1|id) + (1|true_case), d4b %>% filter(condition != "message"))
summary(m5)
standardized_result <- standardize_parameters(m5)
print(standardized_result)
m6 <- lmer(mean ~ condition + (1|id) + (1|true_case), d4b %>% filter(condition != "relevant"))
summary(m6)
m7 <- lmer(mean ~ condition + (1|id) + (1|true_case), d4b %>% filter(condition != "irrelevant"))
summary(m7)
standardized_result <- standardize_parameters(m7)
print(standardized_result)

#corrected p-values
p <- c(0.00000017356, 0.411, 0.00000000647, 0.01009, 0.00334)
p.adjust(p, method = "holm")
```

##Study 4c (posttest)

###Study 4c: Clean
```{r}
df_dirty <- read.csv("Study4c.csv") %>% 
  filter(Finished == 1)

df_dirty <- df_dirty %>%
  filter(if_all(matches("^...x"), ~ .x == 4 | is.na(.x) | .x == ""))

data_cleaned <- df_dirty %>%
  dplyr::select(id, matches("X\\d+_(x|v|p|i|u|a)\\.\\d+_(s|m|b|f)"))

data_long <- data_cleaned %>%
  pivot_longer(cols = -c(id),
               names_to = c("case", "question", "type", "stimulus"),
               names_pattern = "X(\\d+)_(v|p|i|u|a)\\.(\\d)_(.)",
               values_to = "score") %>%
  filter(score != "")

data_summary <- data_long %>%
  filter(!is.na(score)) %>%  
  group_by(id, case, type, stimulus) %>%
  summarize(mean = mean(as.numeric(score), na.rm = TRUE), .groups = 'drop')

d4c <- data_summary %>%
  mutate(stimulus = case_when(
    stimulus == "s" ~ "vienna",
    stimulus == "m" ~ "blockbuster",
    stimulus == "b" ~ "bike",
    stimulus == "f" ~ "merrick"
  )) %>%
  mutate(condition = case_when(
    type == "2" ~ "SD",
    type == "3" ~ "mean"
  )) %>%
  mutate(true_case = paste0(case, type, substr(stimulus, nchar(stimulus), nchar(stimulus)))) %>% 
  dplyr::select(-case, -type) %>% 
  filter(stimulus != is.na(stimulus))
```


###Study 4c: Analyze
```{r}
m <- lmer(mean ~ condition + (1|id) + (1|true_case) + (1|stimulus), d4c)
summary(m)

standardized_result <- standardize_parameters(m)
print(standardized_result)
```

##Study 4d (posttest)

###Study 4d: Clean
```{r}
df_dirty <- read.csv("Study4d.csv") %>% 
  filter(Finished == 1)

d4d <- df_dirty %>% 
  dplyr::select(id, matches("^(irr|rel)"))

d4d <- d4d %>% 
  pivot_longer(cols = -id,
               names_to = "names",
               values_to = "scores") %>%
  separate(names, into = c("condition", "question", "stimulus"), sep = "\\.")

d4d <- d4d %>% 
  filter(scores != "") %>% 
  mutate(scores = as.numeric(scores)) %>% 
  pivot_wider(names_from = question, values_from = scores)

d4d <- d4d %>% 
  group_by(id, condition, stimulus) %>% 
  mutate(interest = ((int + share + surp + mem + eng) / 5))
```

###Study 4d: Analyze
```{r}
m <- lmer(interest ~ condition + (1|stimulus), d4d)
summary(m)

standardized_result <- standardize_parameters(m)
print(standardized_result)

# # # Scale Validity # # #
items <- d4d[, c("int", "share", "surp", "mem", "eng")]
alpha(items)
```














#STUDY 5

##Study 5: Load and clean data
```{r}
df_dirty <- read.csv("Study5.csv") %>% 
  filter(Finished == 1)

df_dirty <- df_dirty %>%
  filter(if_all(matches("^x"), ~ .x == 4 | is.na(.x) | .x == ""))

data_cleaned <- df_dirty %>%
  dplyr::select(id, matches("^(x|v|p|i|u|a|q1|q2)"), -Progress, -UserLanguage)

data_cleaned <- data_cleaned %>% 
  mutate(q1 = as.numeric(ifelse(is.na(q1) | q1 == "", 0, q1))) %>% 
  mutate(q1.1 = as.numeric(ifelse(is.na(q1.1) | q1.1 == "", 0, q1.1))) %>% 
  mutate(q1 = q1 + q1.1) %>% 
  dplyr::select(-q1.1)

data_long <- data_cleaned %>%
  pivot_longer(cols = -c(id, q1, q2),
               names_to = c("question", "condition"),
               names_pattern = "(v|p|i|u|a)\\.(\\d+)",
               values_to = "score") %>%
  filter(score != "") %>% 
  filter(condition != is.na(condition))

data_summary <- data_long %>%
  group_by(id, condition, q1, q2) %>%
  summarize(mean = mean(as.numeric(score), na.rm = TRUE), .groups = 'drop')

d5 <- data_summary %>%
  mutate(condition = case_when(
    condition == "1" ~ "message.opening_unsatisfying.solution",
    condition == "2" ~ "message.opening_satisfying.solution",
    condition == "3" ~ "case.opening_unsatisfying.solution",
    condition == "4" ~ "case.opening_satisfying.solution"
  )) %>% 
  separate(condition, into = c("problem", "solution"), sep = "_", remove = FALSE) %>% 
  mutate(q1 = as.numeric(q1)) %>% 
  mutate(q2 = as.numeric(q2))
```

##Study 5: Analysis
```{r}
# # # Pre-registered # # #
# are satisfying-solutions more curiosity-satisfying? (manipulation check)
m <- Anova(lm(q2 ~ solution, data = d5), type = 2)
m
#effect size
effect_sizes <- eta_squared(m, partial = TRUE)
effect_sizes

# are case-openings more curiosity-provoking?
m <- Anova(lm(q1 ~ problem, data = d5), type = 2)
m
#effect size
effect_sizes <- eta_squared(m, partial = TRUE)
effect_sizes

# case-message X satisfying-solution
m <- Anova(lm(mean ~ problem * solution, data = d5), type = 3)
m
#effect size
effect_sizes <- eta_squared(m, partial = TRUE)
effect_sizes
# interaction is not significant -> type 2
m <- Anova(lm(mean ~ problem * solution, data = d5), type = 2)
m
#effect size
effect_sizes <- eta_squared(m, partial = TRUE)
effect_sizes





# # # exploratory # # #
#holm correction
p <- c(0.936, 0.00000542, 0.152, 0.0118, 0.000000000236)
p.adjust(p, method = "holm")

summary(lm(mean ~ q1, data = d5))
```

##Study 5: Visualize

```{r}
#set order
d5 <- d5 %>% 
  mutate(solution = case_when(solution == "unsatisfying.solution" ~ "unsatisfying resolution",
                            solution == "satisfying.solution" ~ "satisfying resolution"),
         problem = case_when(problem == "message.opening" ~ "message opening",
                            problem == "case.opening" ~ "case opening"),
          problem = factor(problem, levels = c("message opening", "case opening")))

ggplot(d5, aes(x = solution, y = mean, fill = problem)) +
  geom_violin(alpha = 0.2, color = "#D3D3D3") +
  geom_point(position = position_jitter(width = 0.2, height = 0.1), 
             size = 3.5, shape = 21, alpha = 0.15) +
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width = 0, color = "#333333", linewidth = 1.5) +
    stat_summary(fun = mean, geom = "line", aes(group = 1), color = "#333333", linewidth = 2, alpha = 0.7) +
  stat_summary(fun = mean, geom = "point", size = 3, color = "#333333", shape = 21, fill = "white") +

  facet_wrap(~problem) +
  scale_fill_manual(values = c("message opening" = "#4C72B0", "case opening" = "#55A868")) +
  labs(x = "", y = "Mean Insight Score", title = "") +
  theme_minimal() +
  theme(
    legend.position = "none", 
    text = element_text(size = 14, family = "Arial"),
    axis.title.x = element_text(margin = margin(t = 10)),
    axis.title.y = element_text(margin = margin(r = 10)),
    strip.text = element_text(face = "bold")
  )
```







#STUDY 6

##Study 6: Load and clean data

```{r}
d6 <- read.csv("Study6.csv") %>% 
  slice(-c(1:2)) %>% 
  # attention
  mutate(across(starts_with("x"), ~ as.numeric(.x))) %>% 
  filter(if_all(starts_with("x"), ~ .x == 4 | is.na(.x))) %>% 
  # 2. useful = mean of columns starting with v, p, i, u, a
  mutate(across(starts_with(c("v.", "p.", "i.", "u.", "a.")), as.numeric)) %>%
  mutate(useful = rowMeans(across(starts_with(c("v.", "p.", "i.", "u.", "a."))),
                           na.rm = TRUE)) %>%
  
  # 3. generalizable = mean of columns starting with d, s, g
  mutate(across(starts_with(c("d.", "s.", "g.")), as.numeric)) %>%
  mutate(generalizable = rowMeans(across(starts_with(c("d.", "s.", "g."))),
                                  na.rm = TRUE)) %>% 
  
  filter(useful != is.na(useful)) %>% 
  mutate(condition = FL_441_DO) %>% 
  dplyr::select(id, condition, useful, generalizable)
```

##Study 6: Analysis

```{r}
# useful
m <- lm(useful~condition, d6)
anova_type2 <- Anova(m, type = 2)
anova_type2
effect_sizes <- eta_squared(m)
effect_sizes
emm<- emmeans(m, pairwise ~ condition, adjust = "holm")
emm
eff <- eff_size(emm, sigma = sigma(m), edf = df.residual(m), method = "d")
eff

# generalizable
m <- lm(generalizable~condition, d6)
anova_type2 <- Anova(m, type = 2)
anova_type2
effect_sizes <- eta_squared(m)
effect_sizes
emm<- emmeans(m, pairwise ~ condition, adjust = "holm")
emm
eff <- eff_size(emm, sigma = sigma(m), edf = df.residual(m), method = "d")
eff
```

##Study 6: Visualize

```{r}
# rename + order
d6 <- d6 %>%
  mutate(condition = dplyr::recode(condition,
      "Velcrogeneral"    = "General",
      "Velcroparticular" = "Particular",
      "Velcromessage"    = "Message"),
    condition = factor(condition, levels = c("General", "Particular", "Message")))

velcro_cols <- c("General" = "#55A868", "Particular" = "#DD8452",  "Message" = "#4C72B0")


useful <- ggplot(d6, aes(x = condition, y = useful, fill = condition)) +
  geom_violin(alpha = 0.20, color = "#D3D3D3") +
  geom_point(
    position = position_jitter(width = 0.2, height = 0.1),
    size = 3.5, shape = 21, alpha = 0.15
  ) +
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar",
               width = 0, color = "#333333", linewidth = 1.5) +
  stat_summary(fun = mean, geom = "point",
               size = 3, color = "#333333", shape = 21, fill = "white") +
  scale_fill_manual(values = velcro_cols) +
  labs(x = "", y = "Mean Insight Score", title = "") +
  theme_minimal() +
  theme(
    legend.position = "none",
    text = element_text(size = 14, family = "Arial"),
    axis.title.x = element_text(margin = margin(t = 10)),
    axis.title.y = element_text(margin = margin(r = 10))
  )

generalizable <- ggplot(d6, aes(x = condition, y = useful, fill = condition)) +
  geom_violin(alpha = 0.20, color = "#D3D3D3") +
  geom_point(
    position = position_jitter(width = 0.2, height = 0.1),
    size = 3.5, shape = 21, alpha = 0.15
  ) +
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar",
               width = 0, color = "#333333", linewidth = 1.5) +
  stat_summary(fun = mean, geom = "point",
               size = 3, color = "#333333", shape = 21, fill = "white") +
  scale_fill_manual(values = velcro_cols) +
  labs(x = "", y = "Mean Generalizablility Score", title = "") +
  theme_minimal() +
  theme(
    legend.position = "none",
    text = element_text(size = 14, family = "Arial"),
    axis.title.x = element_text(margin = margin(t = 10)),
    axis.title.y = element_text(margin = margin(r = 10))
  )

useful / generalizable
```


# General Discussion

```{r}
# unite study 1 a and b
d1 <- d1a %>% 
  filter(time == 1) %>% 
  dplyr::select(condition, x) %>%
  mutate(study = 1) %>% 
  rbind(d1b %>%
          dplyr::select(condition, x) %>% 
          mutate(study = 2))

m <- lm(x ~ study, d1 %>% 
            filter((condition == "case" & study == 1) |
                     (condition == "message" & study == 2)))
summary(m)

# unite study 2 a and b
d2 <- d2a %>% 
  dplyr::select(stimulus_set, condition, x) %>%
  mutate(study = 1) %>% 
  rbind(d2b %>%
          dplyr::select(stimulus_set, condition, x) %>% 
          mutate(study = 2))

m <- lmer(x ~ study + (1|stimulus_set), d2 %>% filter(!(condition == "message" & study == 1)))
summary(m)
m <- lmer(x ~ study + (1|stimulus_set), d2 %>% 
            filter((condition == "case" & study == 1) |
                     (condition == "message" & study == 2)))
summary(m)

# unite study 4 a and b
d4 <- d4a %>% 
  dplyr::select(stimulus, condition, mean, report) %>%
  mutate(study = 1) %>% 
  rbind(d4b %>%
          mutate(report = 1) %>% 
          dplyr::select(stimulus, condition, mean, report) %>% 
          mutate(study = 2))

m <- lmer(mean ~ study + (1|stimulus), d4 %>% 
            filter((condition == "relevant" & study == 1) |
                     (condition == "message" & study == 2)))
summary(m)
m <- lmer(mean ~ study + (1|stimulus), d4 %>% 
            filter(report == "message" | report == 1))
summary(m)
```


#Appendix
##For Study 1b: Randomly select participant responses
```{r}
#dataset with reported
d.p <- read.csv("Study1a.csv") %>% 
  filter(Finished == 1)

d.q <- d.p %>%
  pivot_longer(cols = starts_with(c("a.", "i.", "u.", "p.", "v.")),
               names_to = c(".value", "category"),
               names_sep = "\\.",
               values_drop_na = TRUE) %>% 
  dplyr::select(id, category, a, q) %>% 
  mutate(category = dplyr::recode(category,
                           "g1" = "general 1",
                           "g2" = "general 2",
                           "n1" = "narrative 1",
                           "n2" = "narrative 2")) %>% 
  separate(col = category, into = c("condition", "time"), sep = " ") %>%
  mutate(condition = as.factor(condition), time = as.factor(time)) %>% 
  filter(time == 1)

#case reports csv
d.case <- d.q %>% 
  filter(condition == "narrative") 
case.reports <- data.frame(sample(d.case$q, 10))
write.csv(case.reports, file = "case.reports.csv", row.names = F)

#message reports csv
d.message <- d.q %>% 
  filter(condition == "general")
message.reports <- data.frame(sample(d.message$q, 10))
write.csv(message.reports, file = "message.reports.csv", row.names = F)
```

##For Study 2b: Randomly select participant responses
```{r}
d.p <- read.csv("Study2a.csv") %>% 
  filter(Finished == 1)

#dataset with reported
d.z <- d.p %>%
  filter(att_t == "4" | is.na(att_t)) %>% 
  filter(att_s == "4" | is.na(att_s)) %>% 
  pivot_longer(cols = starts_with(c("a.", "i.", "u.", "p.", "v.")),
               names_to = c(".value", "item"),
               names_sep = "\\_", 
               values_drop_na = TRUE) %>% 
  pivot_longer(cols = starts_with(c("a.", "i.", "u.", "p.", "v.")),
               names_to = c(".value", "condition"),
               names_sep = "\\.",
               values_drop_na = TRUE) %>% 
  dplyr::select(id, item, condition, a, z) %>% 
  mutate(condition = dplyr::recode(condition,
                           "c1" = "case",
                           "m1" = "message")) %>% 
  mutate(condition = as.factor(condition)) %>%
  mutate(item = dplyr::recode(item,
                            "s" = "Semmelweis",
                            "t" = "Dominos"))

#case-Semmelweis reports csv
d.cv <- d.z %>% 
  filter(condition == "case", item == "Semmelweis") 
cv.reports <- data.frame(sample(d.cv$z, 10))
write.csv(cv.reports, file = "cv.reports.csv", row.names = F)

#case-Dominos reports csv
d.cd <- d.z %>% 
  filter(condition == "case", item == "Dominos") 
cd.reports <- data.frame(sample(d.cd$z, 10))
write.csv(cd.reports, file = "cd.reports.csv", row.names = F)

#message-Semmelweis reports csv
d.mv <- d.z %>% 
  filter(condition == "message", item == "Semmelweis") 
mv.reports <- data.frame(sample(d.mv$z, 10))
write.csv(mv.reports, file = "mv.reports.csv", row.names = F)

#message-Semmelweis reports csv
d.md <- d.z %>% 
  filter(condition == "message", item == "Semmelweis") 
md.reports <- data.frame(sample(d.md$z, 10))
write.csv(md.reports, file = "md.reports.csv", row.names = F)
```

##For Study 3b: Randomly select participant responses
```{r}
#clean study 3 post dataset
d.p <- read.csv("Study3post.csv")
d3post <- d.p %>%
  slice(-c(1:6)) %>% 
  mutate(across(c(Q1, Q2, Q3, Q4, Q5, Q6, a, i, u, p, v), as.numeric)) %>% 
  mutate(post_test_score = (Q1 + Q2 + Q3 + Q4 + Q5 + Q6) / 6) %>% 
  mutate(x = (a+i+u+p+v)/5) %>% 
  dplyr::select(name, post_test_score, x, learn) %>% 
  group_by(name) %>%
  filter(n() == 1) %>%
  ungroup()

#now we compute the mean
s3_mean <- mean(d3post$x)
s3_sd <- sd(d3post$x)

#then we break into the 1SD + and mean +/- 0.5 SD group
d3_insightful <- d3post %>% 
  filter(x > (s3_mean + s3_sd))

d3_uninsightful <- d3post %>% 
  filter(x < (s3_mean + s3_sd/2) & x > (s3_mean - s3_sd/2))

#offer arguments to for loop
datasets <- list(d3_insightful = d3_insightful, 
                 d3_uninsightful = d3_uninsightful)
output_files <- c("d3_sampled_insightful.csv", "d3_sampled_uninsightful.csv")

#sample 10
ten_sample_csv <- function(data, output_file) {
  sampled_data <- sample_n(data, 10)
  write.csv(sampled_data, output_file, row.names = FALSE)
  return(sampled_data)
}

#perform for loop
for (i in seq_along(datasets)) {
  ten_sample_csv(datasets[[i]], output_files[i])
}
```


##For Study 4b: Randomly select participant responses
```{r}
#create dataframes from which to sample
df_messages <- d4a %>% 
  filter(report == "message",
         type == "case")
df_relevant <- d4a %>% 
  filter(report == "relevant",
         type == "case")
df_irrelevant <- d4a %>% 
  filter(report == "irrelevant",
         type == "case")

#offer arguments to for loop
datasets <- list(df_messages = df_messages, 
                 df_relevant = df_relevant, 
                 df_irrelevant = df_irrelevant)
output_files <- c("sampled_messages.csv", "sampled_relevant.csv", "sampled_irrelevant.csv")

#function that pulls precisely 12 reports
even_sample_csv <- function(data, output_file) {
  # For each level in 'stimulus', sample 2.5% of the rows
  sampled_data <- data %>%
    group_by(stimulus) %>%
    sample_frac(0.1 / n_distinct(stimulus)) %>%
    ungroup()
  write.csv(sampled_data, output_file, row.names = FALSE)
  return(sampled_data)
}

#perform for loop
for (i in seq_along(datasets)) {
  even_sample_csv(datasets[[i]], output_files[i])
}
```

##For Study 4c: Randomly select participant responses
```{r}
#first we obtain means
df_relevant <- d4a %>% 
  filter(report == "relevant",
         type == "case")
df_means <- df_relevant %>% 
  group_by(type, condition) %>% 
  summarize(mean_mean = mean(mean), sd = sd(mean)) %>% 
  ungroup()

#then we break into the 1SD + and mean +/- 0.5 SD group
df_insightful <- df_relevant %>% 
  filter(mean >= 6.431382)

df_uninsightful <- df_relevant %>% 
  filter(mean < 5.706726 & mean > 4.257413)

#offer arguments to for loop
datasets <- list(df_insightful = df_insightful, 
                 df_uninsightful = df_uninsightful)
output_files <- c("sampled_insightful.csv", "sampled_uninsightful.csv")

#designed to pull precisely 12 reports
even_sample_csv <- function(data, output_file) {
  sampled_data <- data %>%
    group_by(stimulus) %>%
    sample_n(3) %>% 
    ungroup()
  write.csv(sampled_data, output_file, row.names = FALSE)
  return(sampled_data)
}

#perform for loop
for (i in seq_along(datasets)) {
  even_sample_csv(datasets[[i]], output_files[i])
}
```

##For all studies -- demographic data
```{r}
#Study 1a
d1ad <- read.csv("Study1a_demo.csv")

mean(d1ad$Age)
sd(d1ad$Age)
table(d1ad$Sex)
table(d1ad$Ethnicity.simplified)

#Study 1b
d1bd <- read.csv("Study1b_demo.csv")

mean(d1bd$Age)
sd(d1bd$Age)
table(d1bd$Sex)
table(d1bd$Ethnicity.simplified)

#Study 2a
d2ad <- read.csv("Study2a_demo.csv")

mean(d2ad$Age)
sd(d2ad$Age)
table(d2ad$Sex)
table(d2ad$Ethnicity.simplified)

#Study 2b
d2bd <- read.csv("Study2b_demo.csv")

mean(d2bd$Age)
sd(d2bd$Age)
table(d2bd$Sex)
table(d2bd$Ethnicity.simplified)

#Study 3b
d3bd <- read.csv("Study3b_demo.csv")

mean(d3bd$Age)
sd(d3bd$Age)
table(d3bd$Sex)
table(d3bd$Ethnicity.simplified)

#Study 4a
d4ad <- read.csv("Study4a_demo.csv")

mean(d4ad$Age)
sd(d4ad$Age)
table(d4ad$Sex)
table(d4ad$Ethnicity.simplified)

#Study 4b
d4bd <- read.csv("Study4b_demo.csv")

mean(d4bd$Age)
sd(d4bd$Age)
table(d4bd$Sex)
table(d4bd$Ethnicity.simplified)

#Study 4 post-test 1
d4cd <- read.csv("Study4c_demo.csv")

mean(d4cd$Age)
sd(d4cd$Age)
table(d4cd$Sex)
table(d4cd$Ethnicity.simplified)

#Study 4 post-test 2
d4dd <- read.csv("Study4d_demo.csv")

mean(d4dd$Age)
sd(d4dd$Age)
table(d4dd$Sex)
table(d4dd$Ethnicity.simplified)

#Study 5
d5d <- read.csv("Study5_demo.csv")

mean(d5d$Age)
sd(d5d$Age)
table(d5d$Sex)
table(d5d$Ethnicity.simplified)

d6d <- read.csv("Study6a_demo.csv")

mean(d6d$Age)
sd(d6d$Age)
table(d6d$Sex)
table(d6d$Ethnicity.simplified)
```

